\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.1.1 & 1.1.2 a

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
Machine learning, and computer vision in particular, have seen a sharp transition in modern times from moving from science fiction movies to a mainstream status, present in the smartphones that sit in each and everybody's pocket. More hidden but even more important to our economy and security, these automated tools are now prominent on the servers that empowers essentially all sectors of our daily life, especially medicine for which it empowers practionners with now diagnostic tools to heal people sooner and better. This particular example illustrates also some important challenges increasingly paced by these tools. One of these is their sensibility to adversarial attacks, that is the sensibility of fire models output to minute changes of the input. This Could rain important issues on the reliability of the results y an automated diagnostic model. More generally, these models back also to offer why it forms a given output for a class of inputs. This back. of generality hinders the general advances and acceptance of these methods for secure-sensitive tasks.

>>>>

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
% 1.1.1
Machine learning, and computer vision in particular, have seen a sharp transition in modern times from moving from science fiction movies to a mainstream status, present in the smartphones that sit in each and everybody's pocket. More hidden but even more important to our economy and security, these automated tools are now prominent on the servers that empowers essentially all sectors of our daily life, especially medicine for which it empowers practionners with now diagnostic tools to heal people sooner and better. This particular example illustrates also some important challenges increasingly paced by these tools. One of these is their sensibility to adversarial attacks, that is the sensibility of fire models output to minute changes of the input. This Could rain important issues on the reliability of the results y an automated diagnostic model. More generally, these models back also to offer why it forms a given output for a class of inputs. This back. of generality hinders the general advances and acceptance of these methods for secure-sensitive tasks.

% 1.1.2 a
Taking some perspective, one remembers that these tools are inherited by theoretical models made to understand the brain. while these first neural network were mainly applied on toy-like problems, they were also offering a growing number of applications in computer vision but also more generally for automating tasks. In particular, convolutional neural networks are inspired by the feed-forward processing observed in the visual pathways of primates and reaches now super-human performances for categorizing images. One challenge with these models is to be able to scale them up for prospective applications, for instance in autonomous driving. Indeed, in such applications, the input does not consist of a single image (let's say of about a M byte) but of a continuous stream of images from multiple cameras.

% 1.1.2 b
